Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-11 ms.qmd
Daling with another comment
Adding some revisions to supp[lement, but I think I will move to main as it's important.

### *Meta-Analysis*
We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers. `r utils::packageVersion("metafor")` @Viechtbauer2010-fn].  We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers. 2.0, @Nakagawa2021-ls; @nakagawaorchard]. In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz]. For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution. We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$). We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$). We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian). We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more. If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.

@@

>>>>

### *Meta-Analysis*
We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers. `r utils::packageVersion("metafor")` @Viechtbauer2010-fn].  We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers. 2.0, @Nakagawa2021-ls; @nakagawaorchard]. In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz]. In all cases, frequentist and Bayesian models resulted in the same conclusions. For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution. We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$). We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$). We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian). We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more. If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.

@@

#### Exploring the impact of temperature on $lnRR_{Q_{10}}$ PROBABLY JUST MOVE TO THE MAIN TEXT

$lnRR_{Q_{10}}$, $lnCVR_{Q_{10}}$ and $lnVR_{Q_{10}}$, as with $Q_{10}$ more generally, all assume that the effect of temperature on physiological rates is linear on the log scale. While $Q_{10}$ has been used exstensively in the physiological literature, there is a preference for using a Boltzmann – Arrhenius relationship to model temperature effects because it has been suggested to better incorperate the kinetics of chemical reactions [@gillooly2001effects]. Over biologically realistic temperature ranges the Boltzmann – Arrhenius relationship and van't Hoff approaches can vary by as much as 15%. Despite this, @white2012information compared modelling the temperature-dependent effects on metabolic rate using both the Boltzmann – Arrhenius relationship and van't Hoff ($Q_{10}$) relationship, showing that, when prokaryotes are excluded, the van't Hoff equation provides a 5.8 fold better fit to the data than the Boltzmann – Arrhenius relationship. Given that we restricted studies only to those that manipulated temperatures within normal operating ranges for a species and we only focus on eukaryotes, $Q_{10}$ should remain an appropriate way to capcture temperature dependent effects. However, given that it is not possible to collect full thermal performance curves for species within our data it was not strickly possible to validate this assumption directly. As such, we conducted a series of additonal analyses to better understand when the log-linearity assumption may be violated.

First, we took the maximum temperature of the experimental manipulations and include this temperature in the models. If log-linearity is a problem, $lnRR_{Q_{10}}$ should be underestimated for studies applying higher temperature treatments because such temperatures are expected to either converge on or cross the thermal optima. The benefit of such an approach means that we are able to statistically correct for the potential non-linearity in the data.

Second, we explored the lowest 25% of $lnRR_{Q_{10}}$ values to understand if these studies have high relative tempereatures compared to the Topt for the species or if they have abnormally high temps. Lab and wild can be used.
		3. Using wild populations, extract the temperature time series across the year (range, mean, SD) and compare the temperature manipulations done in the study to those in nature. Do they fall within the range? How far are they from their upper temperatures?
		4. Using the difference between the upper temperatures in nature to the upper temperature of the experiment, include this as a moderator to explore if the deviation from natural conditions covaries with Q10.

```{r, lnrrq10_nonlinear}

# Subset the data
lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
                                     max_temp_c = scale(temp_2, scale = FALSE))

rerun = FALSE
if(rerun){
  model1.1_nl <- metafor::rma.mv(effect_size ~ max_temp_c, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

  model1.1_bayes_nl <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + mid_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  # Save model1.1_nl
  saveRDS(model1.1_nl, file = "./output/models/lnRRQ10_1.1_nl")
  saveRDS(model1.1_bayes_nl, file = "./output/models/lnRRQ10_1.1_bayes_nl")
} else{ 
  model1.1_nl <- readRDS("./output/models/lnRRQ10_1.1_nl")
model1.1_bayes_nl <- readRDS("./output/models/lnRRQ10_1.1_bayes_nl")
}
